 

### 2019-01-28 Manuscript/Plots/survivaldiffSE.tex
Update manuscript

% Created by tikzDevice version 0.11 on 2018-09-18 14:43:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,198.38) --
	( 95.77,197.84) --
	(112.40,196.49) --
	(129.03,194.01) --
	(145.66,190.14) --
	(162.29,184.70) --
	(178.92,177.62) --
	(195.55,168.93) --
	(212.18,158.83) --
	(228.81,147.63) --
	(245.44,135.76) --
	(262.07,123.72) --
	(278.70,112.05) --
	(295.33,101.23) --
	(311.96, 91.68) --
	(328.59, 83.63) --
	(345.22, 77.20) --
	(361.85, 72.33) --
	(378.49, 68.84) --
	(395.12, 66.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,196.04) --
	( 95.77,190.46) --
	(112.40,182.63) --
	(129.03,173.19) --
	(145.66,162.73) --
	(162.29,151.74) --
	(178.92,140.68) --
	(195.55,129.91) --
	(212.18,119.75) --
	(228.81,110.39) --
	(245.44,101.97) --
	(262.07, 94.57) --
	(278.70, 88.20) --
	(295.33, 82.82) --
	(311.96, 78.36) --
	(328.59, 74.74) --
	(345.22, 71.84) --
	(361.85, 69.57) --
	(378.49, 67.81) --
	(395.12, 66.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,198.08) --
	( 95.77,196.53) --
	(112.40,193.46) --
	(129.03,188.72) --
	(145.66,182.27) --
	(162.29,174.23) --
	(178.92,164.82) --
	(195.55,154.36) --
	(212.18,143.26) --
	(228.81,131.93) --
	(245.44,120.83) --
	(262.07,110.32) --
	(278.70,100.74) --
	(295.33, 92.29) --
	(311.96, 85.12) --
	(328.59, 79.23) --
	(345.22, 74.56) --
	(361.85, 70.98) --
	(378.49, 68.35) --
	(395.12, 66.47);

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (331.33,183.02) {min(SE)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (331.33,171.02) {median(SE)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (331.33,159.02) {max(SE)};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.11 on 2019-01-11 16:36:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,197.09) --
	( 95.77,194.00) --
	(112.40,189.53) --
	(129.03,183.87) --
	(145.66,177.12) --
	(162.29,169.41) --
	(178.92,160.85) --
	(195.55,151.61) --
	(212.18,141.85) --
	(228.81,131.78) --
	(245.44,121.67) --
	(262.07,111.79) --
	(278.70,102.46) --
	(295.33, 93.93) --
	(311.96, 86.45) --
	(328.59, 80.16) --
	(345.22, 75.11) --
	(361.85, 71.25) --
	(378.49, 68.43) --
	(395.12, 66.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,196.69) --
	( 95.77,192.37) --
	(112.40,186.05) --
	(129.03,178.13) --
	(145.66,169.03) --
	(162.29,159.10) --
	(178.92,148.73) --
	(195.55,138.24) --
	(212.18,127.94) --
	(228.81,118.07) --
	(245.44,108.86) --
	(262.07,100.46) --
	(278.70, 92.98) --
	(295.33, 86.50) --
	(311.96, 81.02) --
	(328.59, 76.51) --
	(345.22, 72.91) --
	(361.85, 70.12) --
	(378.49, 68.02) --
	(395.12, 66.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,197.17) --
	( 95.77,193.69) --
	(112.40,188.31) --
	(129.03,181.27) --
	(145.66,172.87) --
	(162.29,163.43) --
	(178.92,153.30) --
	(195.55,142.80) --
	(212.18,132.28) --
	(228.81,122.04) --
	(245.44,112.32) --
	(262.07,103.35) --
	(278.70, 95.29) --
	(295.33, 88.25) --
	(311.96, 82.28) --
	(328.59, 77.36) --
	(345.22, 73.43) --
	(361.85, 70.39) --
	(378.49, 68.13) --
	(395.12, 66.48);

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (331.33,183.02) {low SE};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (331.33,171.02) {average SE};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (331.33,159.02) {high SE};
\end{scope}
\end{tikzpicture}
